Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-04-17 AO_bondedSi.tex
incorporate final DTJ edits, add Acknowledgment section

\emph{More complex underlying gap size distributions-} One key assumption of our gap-as-etalon modeling strategy is that the distribution of gap sizes over the measurement area is bimodal- a gap of size $d$ or zero gap.  This choice was simply a matter of computational simplicity, and any more complicated gap size distribution could easily be dropped in as additional terms in Equation \ref{eqnMix}.  For example, if there is a gradient across the bond, the emergent transmission spectrum will be an admixture of many gaps with various areal coverage fractions.  The full solution becomes an areal integral of Equation \ref{eqFP} normalized by the total measurement area.  Solving for the relative distributions of gaps is highly degenerate, in the same way as we saw in the 2-parameter corner plots of gap depth and fill factor.  We experimented with by-eye fitting parametric distributions of gap sizes, characterized by a maximum and minimum gap size, and a monotonic slope of the distribution.  We found that measurements of very large ($>10\lambda$) gaps with a large gradient offered surprisingly strong constraints on the maximum gap size, because of the conspicuous high frequency Fabry-P\`erot fringes.  For sub-wavelength gaps, the gap size distribution is too degenerate to derive much useful insight on the slope of the distribution.  Specifically, for $d_{max}<\lambda/4$, our simple mixture model will converge on the spectrum of the average gap size, even if the \emph{True} distribution is more complex.  Reducing the measurement area could break some of these degeneracies, if more precision is desired.

\emph{The benefit of the Gaussian process-} We chose to estimate the gap size with a Gaussian process regression, but this is not necessary.  Any model fitting strategy, like least squares or over-plotting a model to data by-hand, will yield an estimate for a gap size.  We tested the benefit of Gaussian process regression by generating synthetic data spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

\emph{DSP vs AR coated front faces- } We have assumed that the Si$-$air interfaces are approximated by Fresnel reflection losses.  If the entrance and exit faces of the bonded samples are AR coated, the incoherent multiple reflection model will have to be modified.  AR coated front and exit faces will result in a larger interface loss for a given gap size than the interface loss computed here.

\emph{How far can this technique go?}  The spectrophotometric precision of our instrument flows down directly to limit the smallest measureable gap size.  This limitation will vary from instrument to instrument.  Our instrument can achieve 10 times better accuracy and precision in double beam mode.  However, the slightly different polarization sensitivity in the different beams caused systematic jumps at the lamp/grating change-over wavelengths.  Agilent offers an adapter to reduce the polarization sensitivity, which mitigates these lamp jumps.  If precisions of 0.02\% could be achieved, gaps $<4$ nm could be reliably measured.  This level begins to be comparable to the effect of interesting physics, like surface roughness and refractive index.  In fact, the van der Waals bond energy could be constrained from these types of measurements \cite{2001JOptA...3...85G}.

\emph{Can this technique be applied to imaging?}  The analysis performed in this article informs smart strategies for using IR imaging for gap detection in bonded Si optics.  First, Equation \ref{eqFP} shows that short wavelengths have the most discerning power for detecting small gaps.  So an IR imaging approach should use the shortest possible wavelength without getting close to the Si absorption cutoff.  This work recommends a 1250$-$1300 nm filter.  Images can then be normalized to the transmission through a DSP sample under identical, nearly collimated lighting conditions.  Lastly, any deficits in flux of a bonded sample can be converted to a gap size $d$, using Equation \ref{eqFP}.  IR imaging will lack the spectral information available in the spectra shown in this article.  The imaging will require exceptional quality of flat-fielding or dithering of the images to reach the precision achieved here with relative ease.

@@

>>>>

\emph{More complex underlying gap size distributions-} One key assumption of our gap-as-etalon modeling strategy is that the distribution of gap sizes over the measurement area is bimodal- a gap of size $d$ or zero gap.  This choice was simply a matter of computational simplicity, and we could easily account for any more complicated gap size distribution by inserting additional terms in Equation \ref{eqnMix}.  For example, if there is a gradient across the bond, the emergent transmission spectrum will be an admixture of many gaps with various areal coverage fractions.  Since the gap sizes are small and the interface takes place within a subregion of constant gap size, the full solution becomes an areal integral of Equation \ref{eqFP} normalized by the total measurement area.  Solving for the relative distributions of gaps is highly degenerate, in the same way as we saw in the 2-parameter corner plots of gap depth and fill factor.  We experimented with by-eye fitting parametric distributions of gap sizes, characterized by a maximum and minimum gap size, and a monotonic slope of the distribution.  For sub-wavelength gaps, the gap size distribution is too degenerate to derive much useful insight on the slope of the distribution.  Specifically, for $d_{max}<\lambda/4$, our simple mixture model will converge on the spectrum of the average gap size, even if the \emph{True} distribution is more complex.  Reducing the measurement area could break some of these degeneracies, if more precision is desired.

\emph{The benefit of the Gaussian process-} We chose to estimate the gap size and fill factor with Gaussian process regression.  Gaussian process regression is not necessary if random errors are much larger than the systematic errors, in which case any model fitting strategy---like least squares or over-plotting a model to data by-hand---will yield an unbiased estimate for the gap size.  We tested the benefit of Gaussian process regression by generating synthetic transmission spectra with known gap size and fill factor, and known covariance structure.  We applied ordinary least squares regression to the synthetic spectra and derived values for $d$ and $f$ that were biased by up to $20\sigma$ or more.  Applying Gaussian process regression recovered the input values to within $1\sigma$.

@@

\emph{DSP vs AR coated front faces- } We have assumed that the Si$-$air interfaces are approximated by Fresnel reflection losses.  If the entrance and exit faces of the bonded samples are AR coated, the incoherent multiple reflection model will have to be modified.  \emph{Equation \ref{eqn:Tetalon} is not valid if the entrance and exit Si interfaces are AR coated.}  Equation \ref{eqn:SiAirMatrix} would have to be altered with the the AR coating's wavelength-dependent transmission, which might not have a simple analytical form.

\emph{How far can this technique go?}  The spectrophotometric precision of our instrument flows down directly to limit the smallest measureable gap size.  This limitation will vary from instrument to instrument.  Our instrument can achieve 10 times better accuracy and precision in double beam mode than in single beam mode.  However, the slightly different polarization sensitivity in the different beams caused systematic jumps at the lamp/grating change-over wavelengths.  Agilent offers an adapter to reduce the polarization sensitivity, which mitigates these lamp jumps.  If precisions of 0.02\% could be achieved, gaps $<4$ nm could be reliably measured.  This level begins to be comparable to the effect of interesting physics, like surface roughness and refractive index.  In fact, the van der Waals bond energy could be constrained from these types of measurements \cite{2001JOptA...3...85G}.

\emph{Can this technique be applied to imaging?}  The analysis performed in this article informs smart strategies for using IR imaging for gap detection in bonded Si optics.  In IR images (Figure \ref{figVS2021_IR_image}), interfacial gaps appear as dark patches.  These dark patches are darker at shorter wavelengths as evinced in Equation \ref{eqFP}, which shows that observations at short wavelengths have the most sensitivity to small gaps.  Therefore an IR imaging approach should use the shortest possible wavelength without getting too close to the Si absorption cutoff.  This work recommends a 1250$-$1300 nm filter.  Table \ref{tbl_FB1250} lists the predicted integrated transmission through a commercially available narrow bandpass filter, FB1250-10, which has center wavelength 1250 nm and full width at half maximum 10 nm.  We calculated the integrated flux by integrating the product of the etalon transmission (Equation \ref{eqn:Tetalon}) with the FB1250-10 filter curve downloaded from the Thorlabs website\footnote{\url{www.thorlabs.com}}.  The filter curve and example gap spectra are shown in Figure \ref{figFB1250-10}.

\begin{figure}[htbp]
\includegraphics[width=0.8\columnwidth]{figs/F1250_10_filter.pdf}
\caption{\label{figFB1250-10} Filter curve and gap spectra.  The Thorlabs FB1250-10 filter transmission curve is shown as the dray shaded region.  We integrate the gap spectra with this filter curve to relate the deficit of flux in IR imaging with the axial extent of interfacial gaps.}
\end{figure}

\input{tbls/tbl_FB1250.tex}

Figure \ref{figFB1250-10_integ} shows the integrated transmission through the FB1250-10 filter for small gaps ($0 < d(\mathrm{nm}) < 50$).  Table \ref{tbl_FB1250} and Figure \ref{figFB1250-10_integ} can be used as a look-up table for converting between the dark patches observed in IR imaging and the axial extent of the interface gap, if the FB1250-10 filter is used during IR imaging.  IR images must be normalized to the transmission through a DSP sample under identical, nearly collimated lighting conditions.  Any deficits in flux of a bonded sample can be converted to a gap size $d$, using Table \ref{tbl_FB1250}, if the FB1250-10 filter is used.  IR imaging will lack the spectral information available in the spectra shown in this article.  The curvature of the spectra provides assurance of the physical origin of the dark patches seen in IR imaging.  IR imaging will require exceptional quality of flat-fielding or dithering of the images to reach the precision achieved here with relative ease.

\begin{figure}[htbp]
\includegraphics[width=0.8\columnwidth]{figs/FB1250-10_integ_trans.pdf}
\caption{\label{figFB1250-10_integ} Integrated transmission through the FB1250-10 filter as a function of interface gap size.  The 99.8\% accuracy achieved in this article is shown as the horizontal dashed line.  Imagers that can achieve 5\% photometric accuracy can detect 40 nm gaps.  This figure assumes uncoated Si substrates.}
\end{figure}

@@

Funding information should be listed in a separate block preceding any acknowledgments. List just the funding agencies and any associated grants or project numbers, as shown in the example below:

MGS acknowledges support from Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA ACT grant NNX12AC31G,

The authors thank Amanda Turbyfill, Mike Pavel, and Carleen Boyer for assistance with IR imaging and specroscopy.  MGS thanks the organizers and participants of the \emph{Astro Data Hack Week} (2014), especially Dan Foreman-Mackey for sharing tutorials and code for implementing the Gaussian process technique.  This research has made use of NASA's Astrophysics Data System.  Many of the figures in the paper were made with Matplotlib \citep{Hunter:2007} in IPython Notebooks \citep{PER-GRA:2007}.  The Notebooks with complete version history are available on GitHub\footnote{\url{https://github.com/Echelle/AO_bonding_paper}}.
